To Do List

### 2019-07-08 Papers.Rmd
Add Mourad's distance idea

>>>>

- Mourad, Raphaël. “Studying 3D Genome Evolution Using Genomic Sequence.” Preprint. Bioinformatics, May 23, 2019. https://doi.org/10.1101/646851. - Distance idea - Ratio R of the median distances between convergent CTCF motifs. CTCF sites from ChIP-seq, predicted if not available. R depends on A/B compartments and subcompartments, replication timing, isochores. R can be used to study genome evolution.https://github.com/morphos30/PhyloCTCFLooping
